### 2016-07-17 version0.0/intro0.01.tex
Completed intro.

\section{Prelude}
\label{sec: overview}
%what doIhave inside galaxies:
% stuffIdon't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas.
They all affect each others' formation, evolution, and extinction.
There is also dark matter inside every galaxy, which, to the best of our knowledge, only has gravitational effects on the other components.
Nearly all the information we can obtain from galaxies other than our own comes from their light.
Since each observable phenomenon inside galaxies emits most of its energy in specific wavelengths, 
a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool to understand galaxies. 
Young and evolved stars, dust, and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies. %PB: changed "I" to "we" here - you are talking about the field as a whole, not you in particular

@@

 %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass 
The stellar population synthesis method, which sums stellar spectra to produce a composite spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
A thorough SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs (either by minimizing $\chi^2$ or by Bayesian analysis), using the templates.
One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
Some of the physical properties of galaxies must be assumed as model input find the best SED, and others are derived from SED-fitting results~\citep[see ][for more detail]{Walch08}.
For example, the best-fit SED has information regarding star formation history and stellar mass to light ratio.
By integrating star formation history over a specific time scale, SFR can be derived.
Knowing the stellar mass to light ratio, one can use a galaxy's observed luminosity to calculate its stellar mass.

@@

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
%The total gas mass of galaxies can be determined using optical depth in sub-mm waveband of dust emission. 
In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and have a power-law size distribution.
The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\cite{Peeters04}. %%SR: it is B stars not O ones!
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).

@@

Most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low energy rotational state}(the state of angular momentum, J) and can be excited in the temperature of molecular clouds. %PB: need to fix text in {\bf} earlier in this sentence.
Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
Therefore, $^{12}$CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of molecular clouds dominated by molecular hydrogen~\citep[e.g.][]{Sanders84}.
Higher rotational transitions of CO can be used as a tracer as well, but they are not as common as $J(1\rightarrow 0)$.

@@

\begin{figure}
\label{fig: mco}
\centering
\includegraphics[width=\textwidth]{../image_intro/mvirial_lco.png}
\caption[Relation between the virial mass and CO luminosity]{Relation between the virial mass (M$_{\mathrm{vir}}$) and CO luminosity (L$_{\mathrm{CO}}$) for the Milky Way and extragalactic GMCs. The Milky Way data are shown by dots measured by~\cite{Solomon87}. Black and white symbols correspond to measurements based on $^{12}$CO~($J(2\rightarrow 1)$) and $^{12}$CO~($J(1\rightarrow 0)$), respectively. The black dashed line represents the Galactic mass-luminosity relation (M$_{\mathrm{vir}} \approx 39{\mathrm L}^{0.81}_{\mathrm{CO}}$) with gray region illustrating the Galactic 1$\sigma$ dispersion around the line.
The dot-dashed and blue dashed lines show the fits for dwarf sample and all extragalactic GMCs, respectively.
The extragalactic molecular clouds are very similar to those in the Milky Way. Adapted from~\cite{Bolato08}.}
\end{figure}

In order to empirically determine the relation between H$_2$ masses and CO luminosities, many observational attempts have been made on both Galactic and extragalactic scales. 
One of the most significant studies in this regard was done by~\cite{Solomon87}, who studied this relation over more than 273 clouds inside the Milky Way and found a strong correlation between the virial mass of molecular clouds and CO luminosity. 
In Local Group galaxies, several groups have measured size, line width, and CO luminosity of molecular clouds and investigated the relation between  their virial masses and CO emission in environments other than the Milky Way. 
Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
Fig.~\ref{fig: mco} shows the CO luminosity versus virial masses of molecular clouds in the Milky Way, M31, M33, and IC~10. 
The extragalactic molecular clouds are similar to those in the Milky Way. 
The conversion between the CO luminosity and H$_2$ masses is still a controversial topic~\citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
Problems regarding metallicity are not yet resolved and it is still not clear whether the conversion factor is global or local. 
Extragalactic investigations have been limited to nearby galaxies due to telescope resolution and sensitivity. 
To measure the clouds in distant galaxies, the spatial resolution of maps must be better than 40 pc, which is the typical size of a giant molecular cloud~\citep[e.g.][and references therein]{Young91,Bolato13}.

Atomic gas in galaxies is dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-3}$), along the line-of-sight. %PB: should that be cm$^{-2}$ ?
\begin{equation}
N_{H {\sc I}}  \propto \int T_{\mathrm B} dV
\end{equation}
where $T_{\mathrm B}$ is the temperature brightness in Kelvin and dV is in km~s$^{-1}$, with the integral over the line profile. 
These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.

@@

Extinction happens when there is a combination of both absorption and scattering of radiation by dust.
This effect grows inversely with the wavelength.
Extinction can be defined as a reduction of the original intensity caused by dust:
\begin{equation}
\label{equ: extinction}
{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)\exp[-\tau_{\lambda}],
\end{equation}
where I$(\lambda)$ is observed intensity in wavelength $\lambda$, I$_0(\lambda)$ is intensity of light before passing through dust, and $\tau_{\lambda}$ is extinction at wavelength $\lambda$. %PB: extinction or optical depth?
The extinction also depends on the grain size and extinction cross section.
For measuring SFR using various wavebands, decreasing of the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR.

@@

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
Stellar mass determines the important properties of a star, such as luminosity, lifetime and its evolutionary path. 
One of the most fundamental and difficult questions that a complete theory of star formation must answer is what is the stellar initial mass distribution of a star forming region.
Since most SFR calibrations use emission from stars in a specific mass range, it is necessary to know the stellar IMF to extrapolate to the full stellar population.
\cite{Salpeter55} empirically derived the stellar IMF from the observed stellar luminosity function of the Solar neighbourhood~\citep{Shu87}. 
He introduced a power-law IMF $\Phi$  in the form:
\begin{equation}
\label{equ: salp}
\Phi (\log M) = dN / d \log M \propto M^{-\gamma }
\end{equation} 
where $M$ is the stellar mass, $\gamma$ is a power-law index, and $N$ is the number of stars in the logarithmic mass range of $\log M + d\log M$. %PB should that be $\log $M to $\log M + d\log M$ ? Please check mass range.

@@

\begin{figure}
\label{fig: imf}
\centering
\includegraphics[width=16cm]{../image_intro/imf.png}
\small
\caption[Comparing stellar initial mass functions]{Comparing stellar initial mass functions (IMFs) by plotting the mass fraction per dex, power of 10, versus mass, normalized so that the integral under each curve is unity. The mass ranges from 0.1 to 120~M$_\odot$. Adopted from~\cite{Baldry03}.} 
\end{figure}

@@

\begin{center}
\begin{table}
\caption{Luminosity-to-SFR calibrations adapted from~\cite{Calzetti13}}
\label{table1}
\begin{tabular}{ c c c }
\hline\hline
Luminosity$^1$ & C$^2$ & Assumptions$^3$\\
\hline
L$_{UV}$ & $3.0 \times 10^{(-47)} \lambda$ &$0.1 -100 M_{\odot}, \tau \ge 100 Myr $\\
L$_{UV}$ & $4.2 \times 10^{(-47)} \lambda$ &$0.1 -30 M_{\odot}, \tau \ge 100 Myr $\\
L$_{UV}$ & $4.3 \times 10^{(-47)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 10 Myr $\\
L$_{UV}$ & $1.0 \times 10^{(-46)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $1.6 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $2.8 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $4.1 \times 10^{(-44)}$ &$0.1 -30 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $3.7 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $8.3 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(H${\alpha}$) & $5.5 \times 10^{(-42)}$&$0.1 -100 M_{\odot},  \tau \ge 6 Myr $\\
L(H${\alpha}$) & $3.1 \times 10^{(-41)}$&$0.1 -30 M_{\odot},  \tau \ge 10 Myr $\\
\hline
\end{tabular}
\begin{tablenotes}
\item $^1$ Luminosities (except for UV) are in erg~s$^{-1}$ and are given as $\nu L_{\nu}$.
\item $^2$ The constant $C$ appears in Equ.~\ref{equ: sfrsingle}. For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in $\AA$ to convert luminosity density to luminosity. %or flux density?  
\item $^3$ Assumptions for the mass range of the stellar IMF, using the expression derived by \cite{Kroupa01} (see Section~\ref{sec: imf}), and for the timescale $\tau$.
\end{tablenotes}
\end{table}
\end{center}

The most common single-band tracer of star formation rate is the ultraviolet.
As mentioned before, UV emission is an excellent tracer for the SFR.
Using a spectral energy distribution (SED) from Starburst99, with solar metallicity, and assuming a~\cite{Kroupa01} stellar IMF with the timescale of over 100 Myr, SFR can be measured as~\citep{Leitherer99}:
\begin{equation}
SFR(UV) = 3.0 \times 10^{-47}\lambda L_{\lambda}
\end{equation}
where SFR(UV) is in M$_{\odot}$~yr$^{-1}$, $\lambda$ can be in the range of $(912< \lambda < 3000~\AA$), and $L_{\lambda}$ is in erg s$^{-1}$\AA.
As shown in Table~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few per cent.
The calibration constants' changes for shorter timescales are more significant and 
the their accuracy is 15 per cent which can vary as a function of $\lambda$~\citep{Calzetti13}.
Ultraviolet light can easily be absorbed or scattered by interstellar dust. 
Therefore, using the UV emission as a tracer might lead to underestimation of the SFR if dust extinction corrections are not applied (\cite{Kennicutt12}; also see Section~\ref{sec: ism_intro}).

Another single-band SFR indicator is the emission from hydrogen recombination lines. 
Ionizing photons emitted from young massive stars ionize the surrounding gas. Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ ($0.6563 \mu$m) and H${\beta}$ ($0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators~\citep{Kennicutt98a}. 
The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived using quantum mechanics. 
The assumption is that the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}.
Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorb and re-emit via Ly${\alpha}$ and longer wavelengths.
This is why the H${\alpha}$ emission line strength is greater in optically thick environments. The relation between the SFR, the luminosity of the \halpha emission line, and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
\begin{align}
\label{equ: halpha}
SFR(H\alpha) = 5.5 \times 10^{-42}L(H\alpha) \\
                     = 7.4 \times 10^{-54}Q(H^{\circ})
\end{align}
where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density N$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the \hii~regions. %PB: big $N$ (column density) or small $n$ (number density) ?
Dust extinction (Section~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g. by adding L(24$\mu$m) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.

Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727$\AA$. 
Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity. 
\cite{Gallagher89} calibrated the SFR based on the \oii luminosity by using a sample of 75 galaxies. 
Another calibration for this luminosity was derived by \cite{Kennicutt92}. 
In his review on the SFR,~\citep{Kennicutt98b} averaged these calibrations and derived the following relation:
\begin{equation}
SFR([O\ II]) = 1.4 \times 10^{-41} L([O\ II])
\end{equation}  
where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\oii) is in erg~s$^{-1}$.
Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high-redshift galaxies.
In these galaxies, the \halpha emission line is redshifted out of the optical band.
Consequently, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is very useful~\citep{Kennicutt98b}.

>>>>

\section{Prelude}
\label{sec: overview}
%what doIhave inside galaxies:
% stuffIdon't care about because they don't have a big contribution on the SED 1) planets; 2) black holes 3) dark matter
Inside every galaxy, there are millions of stars, planets, and black holes, as well as dust and gas.
They all affect each others' formation, evolution, and extinction.
There is also dark matter inside every galaxy, which, to the best of our knowledge, only has gravitational effects on the other components.
Nearly all the information we can obtain from galaxies other than our own comes from their light.
Since each observable phenomenon inside galaxies emits most of its energy in specific wavelengths, 
a plot of brightness/flux density of galaxies as a function of wavelength, called a spectral energy distribution (SED), is a useful tool to understand galaxies. 
Young and evolved stars, dust, and gas in the space between the stars are the most important contributors to the spectral energy distributions of galaxies.
Planets and black holes without an accretion disc, on the other hand, have a much lower intensity compared to the other aforementioned components, and therefore contribute less to the SED.
Therefore, with properly modeling observed features in SEDs we can extract information about the evolution of stars, dust, and gas inside galaxies.

@@

 %how do you model it? %SED model CIGALE %Population synthesis ----> SFR, stellar mass 
The stellar population synthesis method, which sums stellar spectra to produce a composite spectrum, has been widely utilized since the 1970s~\citep[e.g.][]{Tinsley72,Searle73} to model SEDs of galaxies.
A thorough SED model must include stellar population models~\citep[e.g.][]{Bruzual93,Bruzual03,Maraston05}, stellar emission and dust attenuation~\citep[e.g.][]{Calzetti00,Dopita05}, dust grain emission such as from polycyclic aromatic hydrocarbons~\citep[PAHs; e.g.][and references therein]{Tielens08}, and IR emission from gas and dust~\citep[e.g.][]{Chary01,Dale02,Lagache03,Lagache04,Smith07a,Draine07}.
Many groups have modelled SEDs for different types of galaxies and created SED templates (for more information see the review of \cite{Walcher11} on fitting of SEDs and references therein).
Since the physical parameters of templates generated by the SED models are known, we can find properties of observed galaxies by fitting their SEDs (either by minimizing $\chi^2$ or by Bayesian analysis), using the templates.
One example of an SED-fitting code is {\em CIGALE}: Code Investigating GALaxy Emission~\citep{Noll09}.
It combines SED models and uses Bayesian analysis to find the best-fit SED for observed data in the rest-frame UV-to-IR.
Some of the physical properties of galaxies must be assumed as model input find the best SED, and others are derived from SED-fitting results~\citep[see ][for more detail]{Walcher08}.
For example, the best-fit SED has information regarding star formation history and stellar mass to light ratio.
By integrating star formation history over a specific time scale, SFR can be derived.
Knowing the stellar mass to light ratio, one can use a galaxy's observed luminosity to calculate its stellar mass.

@@

Dust has an insignificant effect on the mass of the ISM, but it plays crucial roles in the ISM's evolution.
In spiral galaxies, dust grains are located in cold regions ($\sim$30~K) and have a power-law size distribution.
The source of energy for dust thermal emission is heating from stars, and the shape of the continuum depends on size of the grain.
Mid-infrared emission from dust grains is mainly dominated by PAHs heated by evolved stellar population~\cite{Smith07a} or recently formed intermediate-mass young stars~\cite{Peeters04}.
Large grains that are either heated by light from star-forming regions or by the interstellar radiation field from the total stellar population emit most of their light in far-infrared~\citep[e.g.][]{Calapa14, lu14}
Dust is the main source of extinction and reddening of starlight (see Sec.\ref{sec: extinction} for more information).

@@

%Most of our knowledge from molecular clouds comes from observing line emission of CO molecules, which {\bf due to their heavy weight, they have very low energy rotational state}(the state of angular momentum, J) and can be excited in the temperature of molecular clouds. %PB: need to fix text in {\bf} earlier in this sentence.
Most of our knowledge of molecular clouds come from observation of line emission of CO molecules, which, die to their large mass, possess a very low energy rotational state (the state of angular momentum, J) and can be excited in the temperature of molecular clouds. %Sr should I put the \bf back?
Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
Therefore, $^{12}$CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of molecular clouds dominated by molecular hydrogen~\citep[e.g.][]{Sanders84}.
Higher rotational transitions of CO can be used as a tracer as well, but they are not as common as $J(1\rightarrow 0)$.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{../image_intro/mvirial_lco.png}
\caption[Relation between the virial mass and CO luminosity]{Relation between the virial mass (M$_{\mathrm{vir}}$) and CO luminosity (L$_{\mathrm{CO}}$) for the Milky Way and extragalactic GMCs. The Milky Way data are shown by dots measured by~\cite{Solomon87}. Black and white symbols correspond to measurements based on $^{12}$CO~($J(2\rightarrow 1)$) and $^{12}$CO~($J(1\rightarrow 0)$), respectively. The black dashed line represents the Galactic mass-luminosity relation (M$_{\mathrm{vir}} \approx 39{\mathrm L}^{0.81}_{\mathrm{CO}}$) with gray region illustrating the Galactic 1$\sigma$ dispersion around the line.
The dot-dashed and blue dashed lines show the fits for dwarf sample and all extragalactic GMCs, respectively.
The extragalactic molecular clouds are very similar to those in the Milky Way. Adapted from~\cite{Bolato08}.}
\label{fig: mco}
\end{figure}

In order to empirically determine the relation between H$_2$ masses and CO luminosities, many observational attempts have been made on both Galactic and extragalactic scales. 
One of the most significant studies in this regard was done by~\cite{Solomon87}, who studied this relation over more than 273 clouds inside the Milky Way and found a strong correlation between the virial mass of molecular clouds and CO luminosity. 
In Local Group galaxies, several groups have measured size, line width, and CO luminosity of molecular clouds and investigated the relation between  their virial masses and CO emission in environments other than the Milky Way. 
Pioneering works in measuring the extragalactic conversion factor were done for M31 and M32~\citep[e.g.,][]{Wilson89, Wilson90}. 
Fig.~\ref{fig: mco} shows the CO luminosity versus virial masses of the Galactic and extragalactic molecular clouds. 
The extragalactic molecular clouds are similar to those in the Milky Way. 
The conversion between the CO luminosity and H$_2$ masses is still a controversial topic~\citep[e.g.][]{Narayanan11, Bolato13, Sandstrom13}.
Problems regarding metallicity are not yet resolved and it is still not clear whether the conversion factor is global or local. 
Extragalactic investigations have been limited to nearby galaxies due to telescope resolution and sensitivity. 
To measure the clouds in distant galaxies, the spatial resolution of maps must be better than 40~pc, which is the typical size of a giant molecular cloud~\citep[e.g.][and references therein]{Young91,Bolato13}.

Atomic gas in galaxies is dominated by \hi~atoms, which are relatively easy to observe in 21-cm.
Assuming optically thin lines for \hi~emission, the intensity of the 21-cm emission is proportional to the density of the atomic hydrogen, $N_{H {\sc I}}$~(cm$^{-2}$), along the line-of-sight.
\begin{equation}
N_{H {\sc I}}  \propto \int T_{\mathrm B} dV
\end{equation}
where $T_{\mathrm B}$ is the temperature brightness in Kelvin and dV is in km~s$^{-1}$, with the integral over the line profile. 
These properties make the 21-cm line a very useful tool to study gas in the ISM and trace the large-scale distribution of galaxies in the universe (\hi is detectable in most spiral galaxies and some elliptical galaxies).
Although the 21-cm emission is the most reliable technique to map the ISM, the linear relationship between the intensity and the column density of the gas breaks down when the gas is optically thick~\citep{Braun09}.

@@

Extinction happens when there is a combination of both absorption and scattering of radiation by dust.
This effect grows inversely with wavelength.
%Extinction can be defined as a reduction of the original intensity caused by dust:
Extinction is quantified as the difference in observed and initial magnitudes of an object in a specific wavelength ($\lambda$):
\begin{equation}
m_{\lambda} - m_{\lambda}(0) = \mathrm{A}_{\lambda},
\end{equation}
where $\mathrm{A}_{\lambda}$ is the extinction, and $m_{\lambda}$ and $m_{\lambda}(0)$ are observed and initial magnitude, respectively.
Magnitude is related to intensity (I) as:
\begin{equation}
m_{\lambda} = 2.5 \log (I_{\lambda}) + C,
\end{equation}
where c is a constant which depends on photometric system that is being used.
Optical depth, $\tau_{\lambda}$, is defined by ratio of observed and initial intensity of a source as:
\begin{equation}
\label{equ: extinction}
{\mathrm I}(\lambda) = {\mathrm I}_0(\lambda)\exp[-\tau_{\lambda}],
\end{equation}
where I$(\lambda)$ is observed intensity in wavelength $\lambda$ and I$_0(\lambda)$ is intensity of light before passing through dust.
Therefore, the optical depth and extinction can be converted to one an other by $\tau_{\lambda} = 1.086 \mathrm{A}_{\lambda}$. 
The extinction also depends on the grain size and extinction cross section.
For measuring SFR using various wavebands, decreasing of the intensity of radiation must be calculated and corrected for each wavelength; otherwise, there will be an underestimation of SFR.

@@

\subsection{Stellar Initial Mass Function}
\label{sec: imf}
Stellar mass determines the important properties of a star, such as luminosity, lifetime and its evolutionary path. 
One of the most fundamental and difficult questions that a complete theory of star formation must answer is what is the stellar initial mass distribution of a star forming region.
Since most SFR calibrations use emission from stars in a specific mass range, it is necessary to know the stellar IMF to extrapolate to the full stellar population.
\cite{Salpeter55} empirically derived the stellar IMF from the observed stellar luminosity function of the Solar neighbourhood~\citep{Shu87}. 
He introduced a power-law IMF $\Phi$  in the form:
\begin{equation}
\label{equ: salp}
\Phi (\log M) = dN / d \log M \propto M^{-\gamma }
\end{equation} 
where $M$ is the stellar mass, $\gamma$ is a power-law index, and $N$ is the number of stars in the logarithmic mass range of $\log M$ to $\log M + d\log M$.

@@

\begin{figure}
\centering
\includegraphics[width=16cm]{../image_intro/imf.png}
\small
\caption[Comparing stellar initial mass functions]{Comparing stellar initial mass functions (IMFs) by plotting the mass fraction per dex, power of 10, versus mass, normalized so that the integral under each curve is unity. The mass ranges from 0.1 to 120~M$_\odot$. Adopted from~\cite{Baldry03}.} 
\label{fig: imf}
\end{figure}

@@

\begin{table}
\caption{Luminosity-to-SFR calibrations adapted from~\cite{Calzetti13}}
\label{table1}
\begin{center}
\begin{tabular}{ c c c }
\hline\hline
Luminosity$^1$ & C$^2$ & Assumptions$^3$\\
\hline
L$_{UV}$ & $3.0 \times 10^{(-47)} \lambda$ &$0.1 -100 M_{\odot}, \tau \ge 100 Myr $\\
L$_{UV}$ & $4.2 \times 10^{(-47)} \lambda$ &$0.1 -30 M_{\odot}, \tau \ge 100 Myr $\\
L$_{UV}$ & $4.3 \times 10^{(-47)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 10 Myr $\\
L$_{UV}$ & $1.0 \times 10^{(-46)}\lambda$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $1.6 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $2.8 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $4.1 \times 10^{(-44)}$ &$0.1 -30 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $3.7 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(TIR) & $8.3 \times 10^{(-44)}$ &$0.1 -100 M_{\odot}, \tau = 100 Myr $\\
L(H${\alpha}$) & $5.5 \times 10^{(-42)}$&$0.1 -100 M_{\odot},  \tau \ge 6 Myr $\\
L(H${\alpha}$) & $3.1 \times 10^{(-41)}$&$0.1 -30 M_{\odot},  \tau \ge 10 Myr $\\
\hline
\end{tabular}
\end{center}
\begin{tablenotes}
\item $^1$ Luminosities (except for UV) are in erg~s$^{-1}$ and are given as $\nu L_{\nu}$.
\item $^2$ The constant $C$ appears in Equ.~\ref{equ: sfrsingle}. For SFR(UV), the numerical value is multiplied by the wavelength $\lambda$ in \AA to convert luminosity density to luminosity. 
\item $^3$ Assumptions for the mass range of the stellar IMF, using the expression derived by \cite{Kroupa01} (see Section~\ref{sec: imf}), and for the timescale $\tau$.
\end{tablenotes}
\end{table}

The most common single-band tracer of star formation rate is the ultraviolet.
As mentioned before, UV emission is an excellent tracer for the SFR.
Using a spectral energy distribution (SED) from Starburst99, with solar metallicity, and assuming a~\cite{Kroupa01} stellar IMF with the timescale of over 100 Myr, SFR can be measured as~\citep{Leitherer99}:
\begin{equation}
SFR(UV) = 3.0 \times 10^{-47}\lambda L_{\lambda}
\end{equation}
where SFR(UV) is in M$_{\odot}$~yr$^{-1}$, $\lambda$ can be in the range of $(912< \lambda < 3000~$\AA), and $L_{\lambda}$ is in erg s$^{-1}$\AA.
As shown in Table~\ref{table1}, with changes in the stellar ranges of the IMF, during timescales longer than 100 Myr, the calibration constant only decreases by a few per cent.
The calibration constants' changes for shorter timescales are more significant and 
the their accuracy is 15 per cent which can vary as a function of $\lambda$~\citep{Calzetti13}.
Ultraviolet light can easily be absorbed or scattered by interstellar dust. 
Therefore, using the UV emission as a tracer might lead to underestimation of the SFR if dust extinction corrections are not applied (\cite{Kennicutt12}; also see Section~\ref{sec: ism_intro}).

Another single-band SFR indicator is the emission from hydrogen recombination lines. 
Ionizing photons emitted from young massive stars ionize the surrounding gas. Hydrogen recombination line emission, such as the Balmer series lines of H${\alpha}$ ($0.6563 \mu$m) and H${\beta}$ ($0.4861 \mu$m), which are located in the optical wavelength range, are among the most traditional SFR indicators~\citep{Kennicutt98a}. 
The relationship between the intensity of a hydrogen recombination line and the ionizing photon rate for a nebula is derived using quantum mechanics. 
The assumption is that the nebula must be optically thick to ionizing photons~\citep{Osterbrock06}.
Being optically thick means that almost all transitions more energetic than Ly${\alpha}$ absorb and re-emit via Ly${\alpha}$ and longer wavelengths.
This is why the H${\alpha}$ emission line strength is greater in optically thick environments. The relation between the SFR, the luminosity of the \halpha emission line, and the ionizing photon rate is~\citep[e.g.,][]{Osterbrock06, Kennicutt98b}:
\begin{align}
\label{equ: halpha}
SFR(H\alpha) = 5.5 \times 10^{-42}L(H\alpha) \\
                     = 7.4 \times 10^{-54}Q(H^{\circ})
\end{align}
where SFR(\halpha) is in M$_{\odot}$~yr$^{-1}$, L(\halpha) is in erg~s$^{-1}$, and Q(H$^{\circ}$) is the ionizing photon rate in units of s$^{-1}$.
The constant on the right-hand side of Equ.~\ref{equ: halpha} is the resulting coefficient for electron temperature T$_{\mathrm{e}}=10000$~K and density n$_{\mathrm{e}}=100$~cm$^{-3}$ which is typical in the \hii~regions.
Dust extinction (Section~\ref{sec: ism_intro}) is the most important source of systematic error in calculating the SFR from hydrogen recombination lines.
The effects of dust must be measured and \halpha observations must be corrected for extinction (e.g. by adding L(24~$\mu$m) to account for dust emission) or this could lead to underestimating the SFR~\citep{Kennicutt98b}.

Another nebular line used as a tracer of the SFR is \oii~$\lambda$3727~\AA. 
Although the luminosities of forbidden lines do not correlate with the ionizing atoms directly, their extinction has a correlation with the \halpha emission. 
As a result, \oii~luminosity can be used as a tracer of the SFR through \halpha luminosity. 
\cite{Gallagher89} calibrated the SFR based on the \oii luminosity by using a sample of 75 galaxies. 
Another calibration for this luminosity was derived by \cite{Kennicutt92}. 
In his review on the SFR,~\citep{Kennicutt98b} averaged these calibrations and derived the following relation:
\begin{equation}
SFR([O\ II]) = 1.4 \times 10^{-41} L([O\ II])
\end{equation}  
where SFR(\oii) is in M$_{\odot}$~yr$^{-1}$ and L(\oii) is in erg~s$^{-1}$.
Although SFR(\oii) is not as accurate as the SFR(\halpha), it is one of major SFR indicators in high-redshift galaxies.
In these galaxies, the \halpha emission line is redshifted out of the optical band.
Consequently, calibration of the strongest emission feature in the blue (\oii) as an SFR indicator is very useful~\citep{Kennicutt98b}.
